---
title: "rdog"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
devtools::load_all()
```

This is a port of the [zdog](https://zzz.dog/) pseudo 3D engine for R.
Currently a work in progres.

## Installation

``` r
devtools::install_github('oganm/rdog')
```

Install the latest Rstudio to make sure it works well with the built in
viewer. Some elements appears to misbehave in older versions.

## Why?

…

## Basic usage

``` {r}
illustration('illo',dragRotate = TRUE) %>% 
        shape_rect(width = 50, height = 50,stroke = 20, fill = FALSE,rotate = c(z=tau/8)) %>% 
    shape_ellipse(id = 'hede',color = 'red',stroke = 20,width = 120,height = 120,fill = FALSE) %>%
    zfont_font(id = 'font') %>% 
    zfont_text(zfont = 'font',text = 'Text',fontSize = 50,
               textAlign = 'center',stroke = 4,translate = c(y = 110)) %>%
    # animation_none()
    animation_rotate(rotate = c(y = .05)) %>% 
    record_gif(duration = 4)
```


`record_gif` is not required for interactive usage or html renderings. By default, the
output is a tagList, that can be automatically displayed in the viewer. This doesn't work
with github_document's due to restrictions on github so rendering into a gif is necesary.

## Use in shiny

WIP. Syntax below is subject to change since it depends on the `rdog_widget` function. Currently
looking for a way to get rid of that. Also the current version has a bug that causes animations
to speed up whenever there's a change...

```r
library(shiny)
library(rdog)
ui <- fluidPage(
    shiny::sliderInput(min = 0, max = 100, inputId = 'slider',label = '',value = 20),
    rdogOutput('dogy',height = 240,width = 240)
)

server <- function(input, output) {
    output$dogy = renderRdog({
        illustration('illo',dragRotate = TRUE) %>%
            shape_rect(width = 50, height = 50,stroke = input$slider, fill = FALSE,rotate = c(z=tau/8)) %>%
            shape_ellipse(id = 'hede',color = 'red',stroke = input$slider,width = 120,height = 120,fill = FALSE) %>%
            zfont_font(id = 'font') %>%
            zfont_text(zfont = 'font',text = 'Text',fontSize = 50,
                       textAlign = 'center',stroke = 4,translate = c(y = 110)) %>%
            # animation_none()
            animation_rotate(rotate = c(y = .05)) %>%
            rdog_widget()

    })

}

# Run the application
shinyApp(ui = ui, server = server)
```

<!--
Currently the shiny syntax is a little non-standard and it's likely to change. As 
shown in the example below, one has to use `rdogOutput` on the UI code like a regular
shiny UI element, however, instead of using a function like `renderRdog`, instead we
create the rdog illusration inside an `observe` code block and pass the output to
`make_shiny`.


```r
library(shiny)
library(rdog)
ui <- fluidPage(
    shiny::sliderInput(min = 0, max = 100, inputId = 'slider',label = '',value = 20),

    rdogOutput(id = 'canv')
)

server <- function(input, output) {
   observe({
        illustration(id = 'canv') %>%
            shape_ellipse(id = 'hede',color = 'red',stroke = input$slider,width = 120,height = 120,fill = FALSE) %>%
            animation_none() %>%
            make_shiny()
    })

}

shinyApp(ui = ui, server = server)

```
-->

## Use as shiny inputs

WIP
